Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean in the United States

### 2017-10-02 doc/manuscript/manuscript.tex
commiting most recent version of manuscript [skip ci]

We wanted to evaluate patterns of connectivity between shared multilocus
haplotypes across geographic regions. We first tabulated the multilocus
haplotypes shared between at least two populations (defined as states or
countries) with the \emph{poppr} function \texttt{mlg.crosspop()}
(Kamvar et al., 2014). From these data, we constructed a graph with
populations as nodes and shared haplotypes as edges (connections)
between nodes using the R packages \emph{igraph} (Csardi \& Nepusz,
2006), \emph{dplyr} version 0.7.3 (Wickham et al., 2017), and
\emph{purrr} version 0.2.3 (Henry \& Wickham, 2017). Each node was
weighted by the fraction of shared MLHs. Each edge represented a single
MLH, but because a single MLH could be present in more than one
population, that MLH would have a number of edges equivalent to the
total number of possible connections, calculated as
(\emph{n}*(\emph{n}-1))/2 edges where n represents the number of
populations crossed. Edges were weighted by \(1-P_{sex}\), where
\(P_{sex}\) is the probability of encountering the same haplotype via
two independent meiotic events (Parks \& Werth, 1993; Arnaud-Hanod et
al., 2007). This weighting scheme would thus strengthen the connection
of edges that represented genotypes with a low probability of being
produced via sexual reproduction. We then identified communities (among
the Regions) in the graph using the \texttt{cluster\_optimal()} function
from \emph{igraph} (Csardi \& Nepusz, 2006). The graph was plotted using
the R packages \emph{ggplot2} version 2.2.1 (Wickham, 2009) and
\emph{ggraph} 1.0.0 (Pedersen, 2017). To ensure that we captured the
same community signal, we additionally performed this analysis including
the five polymorphic markers described above.

>>>>

We wanted to evaluate patterns of connectivity between shared multilocus
haplotypes across geographic regions. We first tabulated the multilocus
haplotypes shared between at least two populations (defined as states or
countries) with the \emph{poppr} function \texttt{mlg.crosspop()}
(Kamvar et al., 2014). From these data, we constructed a graph with
populations as nodes and shared haplotypes as edges (connections)
between nodes using the R packages \emph{igraph} (Csardi \& Nepusz,
2006), \emph{dplyr} version 0.7.4 (Wickham et al., 2017), and
\emph{purrr} version 0.2.3 (Henry \& Wickham, 2017). Each node was
weighted by the fraction of shared MLHs. Each edge represented a single
MLH, but because a single MLH could be present in more than one
population, that MLH would have a number of edges equivalent to the
total number of possible connections, calculated as
(\emph{n}*(\emph{n}-1))/2 edges where n represents the number of
populations crossed. Edges were weighted by \(1-P_{sex}\), where
\(P_{sex}\) is the probability of encountering the same haplotype via
two independent meiotic events (Parks \& Werth, 1993; Arnaud-Hanod et
al., 2007). This weighting scheme would thus strengthen the connection
of edges that represented genotypes with a low probability of being
produced via sexual reproduction. We then identified communities (among
the Regions) in the graph using the \texttt{cluster\_optimal()} function
from \emph{igraph} (Csardi \& Nepusz, 2006). The graph was plotted using
the R packages \emph{ggplot2} version 2.2.1 (Wickham, 2009) and
\emph{ggraph} 1.0.0 (Pedersen, 2017). To ensure that we captured the
same community signal, we additionally performed this analysis including
the five polymorphic markers described above.
